---
title: "Project 3: PACKAGE_NAME Tutorial"
author: Vanessa Yang
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PACKAGE_NAME Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
This package is for project 3 for STAT302. It contains four functions: 
<p>
* my_t.test
* my_lm
* my_knn_cv
* my_rf_cv
</p>
These models analyze data and evaluate statistical models. It also containts a dataset my_gapminder taken from the gapminder package.
<br>


You can install my package through Github by typing in the console:
```{r install, eval=FALSE}
devtools::install_github("vanessaaaay/package302")
```


To begin, we need to load the following packages and the example dataset.
```{r setup, echo=FALSE, eval=TRUE}
library(package302)
data("my_gapminder")
```


## Tutorials
In the tutorial section, I will demonstrate how to use each function.

### my_t_test
Function *my_t.test}* can be used to perform a one-sample t-test. It's helpful when you want to test the null hypothesis. We are going to make some t-tests here by using **lifeExp**  variable from my_gapminder dataset.
<br>
Suppose I want to test the null hypothesis in which the mean value of lifeExp is 60. So we will set *mu = 60*.
```{r mu}
mu <- 60
```
And:
$$H_0: \mu = 60$$
We also want to set the significant level to 0.05.
$$\alpha = 0.05$$
Now, we are ready to do the t-tests. 

***

First example -- two.tailed t-test:
$$H_a: \mu \neq 60$$
```{r two.sided}
my_t_test(data = my_gapminder$lifeExp, mu, alt = "two.sided")
```
From the output, we can see the t-value, degree of freedom, p-value, and the alternative hypothesis. The p-value obtained is greater than the significant level of 0.05, so we don't reject the null hypothesis.

***

Second example -- one.tailed t-test (less)
$$H_a: \mu < 60$$
```{r less}
my_t_test(data = my_gapminder$lifeExp, mu, alt = "less")
```
The p-value for "less" is less than the significant level of 0.05. Thus, we reject the null hypothesis and accept the alternative hypothesis.

***

Third example -- one.tailed t-test (greater)
```{r greater}
my_t_test(data = my_gapminder$lifeExp, mu, alt = "greater")
```
We don't reject the null hypothesis because the p-value is greater than the significant level of 0.05.




